Appeal of rejection of GCB-20-1713

### 2020-09-17 manuscript/journal_submissions/2020_8_GCB/appeal.Rmd
generated word version, minor edit

---
title: "Appeal of rejection of GCB-20-1713"
output: pdf_document
bibliography: library.bib
csl: global-change-biology.csl
---

@@

We would like to appeal the reject decision of our manuscript "Global patterns of forest autotrophic carbon fluxes" (GCB-20-1713) on the grounds that Reviewer 1 (of 2) was off-base in (1) providing an inaccurate assessment of the scope of our analysis relative to previous studies, (2) under-valuing high-quality synthesis that produces unsurprising results, (3) setting expectations for this type of analysis that are out of line with the state of the field, and (4) recommending a completely inappropriate alternate venue. We detail these objections below:

>>>>

---
title: "Appeal of rejection of GCB-20-1713"
output: word_document
bibliography: library.bib
csl: global-change-biology.csl
---

@@

We would like to appeal the reject decision of our manuscript "Global patterns of forest autotrophic carbon fluxes" (GCB-20-1713) on the grounds that Reviewer 1 (of 2) was off-base in (1) providing an inaccurate assessment of the scope of our analysis relative to previous studies, (2) under-valuing high-quality synthesis that produces unsurprising results, (3) setting expectations for this type of analysis that are out of line with the state of the field, and (4) recommending a completely inappropriate alternate venue. We detail these objections below. We note that Reviewer 2 was supportive, and her/his comments could easily be addressed.
